Title Goes Here

### 2021-04-07 analysis/paper/shceof.Rmd
Corrije la correlación que no aparecía
Closes #14

Since the Real cEOF2 represents just a different phase of the same wave train, one would expect that it would show a similar forcing pattern to the Imaginary cEOF with a slight translation of its location. However, Figure\ \@ref(fig:sst-psi-2).a1 and b1 show that the Real cEOF2 is not associated either with any significant SST nor streamfunction anomalies in the tropics. The correlation between the Real cEOF2 and ENSO is also not significant (`r enso_cor[cEOF == "cEOF2" & part == "Real"]$cor_text`) \textcolor{red}{(No aparece el valor en el PDF)}. This lack of tropical signal suggests different natures of the different phases of the cEOF2 wave train.

>>>>

Since the Real cEOF2 represents just a different phase of the same wave train, one would expect that it would show a similar forcing pattern to the Imaginary cEOF with a slight translation of its location. However, Figure\ \@ref(fig:sst-psi-2).a1 and b1 show that the Real cEOF2 is not associated either with any significant SST nor streamfunction anomalies in the tropics. The correlation between the Real cEOF2 and ENSO is also not significant (`r enso_cor[cEOF == "cEOF2" & part == "Real"]$text`) \textcolor{red}{(No aparece el valor en el PDF)}. This lack of tropical signal suggests different natures of the different phases of the cEOF2 wave train.
